On Principles for Government Open Data Curation

### 2023-06-16 talk/slides.Rmd
added date

---
title: "On Principles for Government Open Data Curation"
author: ""     # to be supplied through headers-includes below
institute: ""  # to be supplied through headers-includes below
output:
  beamer_presentation:
    theme: "AnnArbor"
    colortheme: "dolphin"
    slide_level: 2
#    toc: true
    number_sections: false
classoption: "aspectratio=169"
header-includes:
  - \usepackage{amsmath, amsfonts, bm}
  - \usepackage{hyperref}\hypersetup{colorlinks=true, citecolor=blue}
  - \usepackage{caption}
  - \usepackage{booktabs}
  - \usepackage{multirow}
  - \usepackage{adjustbox}
  - \setbeamercolor{frametitle}{bg=white}
  - \AtBeginSection[]
    {
    \begin{frame}<beamer>
      \frametitle{Outline}
      \tableofcontents[currentsection]
    \end{frame}
    }
  - \AtBeginDocument
    {
    \title[NYC 311 Requests]{On Principles for Government Open Data Curation\\A Case Study with NYC 311 Servece Requests}
    \author[Jun Yan]{David Tussey\inst{1} and Jun Yan\inst{2}}
    \institute[University of Connecticut]{\inst{1} Former Executive Director, NYC DoITT\\
    \inst{2} University of Connecticut}
    }
bibliography: ["../manuscript/ref.bib"]
link-citations: true
link-color: true
# csl: apa.csl
---

>>>>

---
title: "On Principles for Government Open Data Curation"
date: "June 15, 2023 @ GASP23"
author: ""     # to be supplied through headers-includes below
institute: ""  # to be supplied through headers-includes below
output:
  beamer_presentation:
    theme: "AnnArbor"
    colortheme: "dolphin"
    slide_level: 2
#    toc: true
    number_sections: false
classoption: "aspectratio=169"
header-includes:
  - \usepackage{amsmath, amsfonts, bm}
  - \usepackage{hyperref}\hypersetup{colorlinks=true, citecolor=blue}
  - \usepackage{caption}
  - \usepackage{booktabs}
  - \usepackage{multirow}
  - \usepackage{adjustbox}
  - \setbeamercolor{frametitle}{bg=white}
  - \AtBeginSection[]
    {
    \begin{frame}<beamer>
      \frametitle{Outline}
      \tableofcontents[currentsection]
    \end{frame}
    }
  - \AtBeginDocument
    {
    \title[NYC 311 Requests]{On Principles for Government Open Data Curation:\\A Case Study with NYC 311 Servece Requests}
    \author[Jun Yan]{David Tussey\inst{1} and Jun Yan\inst{2}}
    \institute[University of Connecticut]{\inst{1} Former Executive Director, NYC DoITT\\
    \inst{2} University of Connecticut}
    }
bibliography: ["../manuscript/ref.bib"]
link-citations: true
link-color: true
# csl: apa.csl
---
